# Appendix C – Situation Analysis, Strategies, Actions, and Theories of Change {-}

## Situation Alanysis {-}

The following situation model was developed by the WCRP partnership to “map” the project context and brainstorm potential actions for implementation. Green text is used to identify actions that were selected for implementation (see ‘Strategies & Actions’), and red text is used to identify actions that the project team has decided to exclude from the current iteration of the plan, given that they were either outside of the project scope or were deemed to be ineffective by the Planning Team. 

Figure 10: Situation analysis developed by the Planning Team to identify factors that contribute to fragmentation (orange boxes), biophysical results (brown boxes), and potential strategies/actions to improve connectivity (yellow hexagons) for focal species in the Bulkley River watershed. 

## Strategies and Actions {-}

The Planning Team identified four broad strategies to implement through this WCRP: 1) barrier rehabilitation, 2) barrier prevention, 3) strengthen Indigenous connections to land and water, and 4) planning and progress tracking. Individual actions were qualitatively evaluated based on the anticipated effect each action will have on realizing on-the-ground gains in connectivity. Effectiveness ratings are based on a combination of “Feasibility” and ”Impact”. Feasibility is defined as the degree to which the project team can implement the action within realistic constraints (financial, time, ethical, etc.), and Impact is the degree to which the action is likely to contribute to achieving one or more of the goals established in this plan. 

### Strategy 1: Barrier Rehabilitation {-}
Table 16: Strategy 1 – Barrier Rehabilitation. 
```{r  echo = FALSE, results = 'asis'}
#| label: table-16
#| tbl-cap: "Strategy 1: Barrier Rehabilitation "
#| warning: false
#| echo: false

source("Rscripts/table_formatting.R")
library("flextable")

data <- read.csv("data/strategy-barrier-remediation.csv", check.names=FALSE)
ft <- flextable(data)
ft <- format_flextable(ft)
ft
```

### Strategy 2: Lateral Barrier Prevention {-}
Table 17: Strategy 2 – Barrier Prevention
```{r echo = FALSE, results = 'asis'}
#| label: table-17
#| tbl-cap: "Strategy 2: Barrier Prevention"
#| warning: false
#| echo: false

source("Rscripts/table_formatting.R")
library("flextable")

data <- read.csv("data/strategy-barrier-prevention.csv", check.names=FALSE)
ft <- flextable(data)
ft <- format_flextable(ft)
ft
```


### Strategy 3: Strengthen Indigenous connections to land and water{-}

Table 18: Strategy 3 – Strengthen Indigenous connections to land and water
```{r echo = FALSE, results = 'asis'}
#| label: table-17
#| tbl-cap: "Strategy 2: Barrier Prevention"
#| warning: false
#| echo: false

source("Rscripts/table_formatting.R")
library("flextable")

data <- read.csv("data/strategy-barrier-prevention.csv", check.names=FALSE)
ft <- flextable(data)
ft <- format_flextable(ft)
ft
```


## Theories of Change {-}

Theories of Change are explicit assumptions around how the identified actions will achieve gains in freshwater connectivity and contribute towards reaching the goals of the plan. To develop Theories of Change, the Planning Team developed explicit assumptions for each strategy which helped to clarify the rationale used for undertaking actions and provided an opportunity for feedback on invalid assumptions or missing opportunities. The Theories of Change are results oriented and clearly define the expected outcome. The following theory of change models were developed by the WCRP Planning Team to “map” the causal (“if-then”) progression of assumptions of how the actions within a strategy work together to achieve project goals. 