```{python echo=FALSE}
import python.api_calls as api
import pandas as pd
import warnings

warnings.filterwarnings('ignore')
```
```{r}
#| echo: false
#| warning: false

library(reticulate)
api <- import("python.api_calls")
gain <- api$gain

source("Rscripts/table_formatting.R")

```

# Structure Prioritization {-}

## Field Assessment Ranking Process {-}
A primary outcome of the WCRP will be the rehabilitation of barriers to connectivity in the Bulkley River Watershed. To achieve the goals in this plan, it is necessary to identify a suite of barriers that, if rehabilitated, will provide access to a minimum of 86 km of spawning habitat and 211 km of rearing habitat (@tbl-table16):

```{python echo=FALSE}
#| label: tbl-table16
#| tbl-cap: "Spawning and rearing habitat connectivity gain requirements to meet WCRP goals in the Bulkley River watershed. The measures of currently accessible and total habitat values are derived from the Intrinsic Potential habitat model described in Appendix B."
#| warning: false
#| echo: false

# Variables to API calls
connect = api.watershed_connectivity("ALL")[0]
total = round(api.watershed_connectivity("ALL")[1],2) #total km in BULK
access = round(api.watershed_connectivity("ALL")[2],2)
gain = round((total*0.95)-access,2)

connect_spawn = api.watershed_connectivity("SPAWNING")[0]
total_spawn = round(api.watershed_connectivity("SPAWNING")[1],2) #total km in BULK
access_spawn = round(api.watershed_connectivity("SPAWNING")[2],2)
gain_spawn = round((total*0.95)-access,2)

connect_rear = api.watershed_connectivity("REARING")[0]
total_rear = round(api.watershed_connectivity("REARING")[1],2) #total km in BULK
access_rear = round(api.watershed_connectivity("REARING")[2],2)
gain_rear = round((total*0.95)-access,2)

# Data frame with table info
df = pd.DataFrame({"Habitat Type":["Spawning","Rearing"],
                   "Currently accessible (km)":[str(access_spawn),str(access_rear)],
                   "Total": [str(total_spawn),str(total_rear)],
                   "Current Connectivity Status":[str(connect_spawn)+"%",str(connect_rear)+"%"],
                   "Goal": ["95%","80%"],
                   "Gain required (km)": [str(gain_spawn),str(gain_rear)]
                   })

# Apply table styling
styled_df = df.style.hide().set_properties(**{'text-align': 'left'})
# header styling
table_styles = [{
       'selector': 'th',
       'props': [('background-color', '#008270'),('text-align', 'left')]
   }]
styled_df.set_table_styles(table_styles)

```


After all existing data and knowledge are collated for known and modelled crossings, an iterative ranking process is conducted to help confirm barriers to target for rehabilitation to meet the goals. The ranking process is primarily used to guide field assessments and maximize efficiency in ground truthing data inputs and model outputs, while providing a secondary purpose to evaluate the relative key habitat gains of confirmed barriers in the watershed. This process, combined with input from local knowledge holders and experts, is used to develop field plans for assessing barriers that have the potential to block the most key habitat in the watershed.
Field assessments are based on the [BC Fish Passage Strategic Approach](https://www2.gov.bc.ca/assets/gov/environment/plants-animals-and-ecosystems/fish-fish-habitat/fish-passage/strategic20approach20july202014.pdf) and can include a barrier assessment (i.e., evaluating passability of the structure), a habitat confirmation (i.e., evaluation of whether the upstream habitat is suitable for the focal species and whether there are other undocumented anthropogenic or natural barriers upstream or downstream), or a detailed habitat investigation (e.g., a fish passage study or further in-depth analysis of habitat features in a waterbody).
The ranking process accounts for the long-term and immediate potential habitat gains potentially offered by each structure to identify structures that maximize long-term and immediate potential to improve key habitat connectivity in the watershed. All structures in the watershed (excluding those confirmed as passable) are ranked in each iteration of the ranking process. Details of the ranking process used to guide field assessments can be found in Appendix XX.


## Structure Prioritization Summary {-}

Following field assessments, structures are placed on one of five possible lists:

1.	Priority barriers list – the structure is confirmed as a full or partial barrier, has key habitat confirmed to exist upstream, and is considered actionable by the planning team (i.e., action items will be identified to advance rehabilitation of the structure). Depending on the barrier, owner, financial constraints, and quality of upstream habitat, the action may be to leave to end of life cycle before reviewing again, remove and decommission the road, replace with a new passable structure, or modify to temporarily restore connectivity (e.g., fish ladder or baffles installed; Table XX).

2.	Assessed structures that remain data deficient list – some form of field assessment has been completed on the structure, but further investigation is required to confirm either the passability status or presence/suitability of upstream habitat (TABLEXX).

3.	Rehabilitated barriers list – priority barriers that have been addressed (either through removal, replacement, or temporary fish passage improvement projects; Table XX) 

4.	Non-actionable barriers list – the structure is confirmed to be a barrier to fish passage and have some amount/quality of habitat upstream, but the planning team will not identify actions to advance rehabilitation of the structure because of logistic considerations (e.g., financial costs), short habitat gain, or the upstream habitat is of poor quality or unsuitable in its present condition to support key life stages of the focal species (Appendix XX).

5.	Excluded structures list – the structure is excluded from further consideration in subsequent ranking and work planning because the structure is confirmed passable (e.g., bridge), not present, or there is no key habitat upstream (Appendix XX).

```{r rehab, echo = FALSE, results = 'asis'}
#| label: tbl-confirmed
#| tbl-cap: "Confirmed barriers"
#| warning: false
#| echo: false

data <- read.csv("data/confirmed_barriers.csv", check.names=FALSE)
ft <- flextable(data)
ft <- format_flextable(ft)
ft
```

```{r rehab, echo = FALSE, results = 'asis'}
#| label: tbl-datadeficient
#| tbl-cap: "Data Deficient Structures"
#| warning: false
#| echo: false

data <- read.csv("data/assessed_strucDD.csv", check.names=FALSE)
ft <- flextable(data)
ft <- format_flextable(ft)
ft
```


```{r rehab, echo = FALSE, results = 'asis'}
#| label: tbl-rehabilitated
#| tbl-cap: "Rehabilitated Structures"
#| warning: false
#| echo: false

data <- read.csv("data/rehabilitated_barriers.csv", check.names=FALSE)
ft <- flextable(data)
ft <- format_flextable(ft)
ft
```

```{r removed-from-consideration, echo = FALSE, results = 'asis'}
#| label: tbl-removed-from-consideration
#| tbl-cap: "List of structures that were removed from the barrier prioritization list following field assessment. Structures include those prioritized as part of the first iteration of the intermediate barrier list and additional sites selected by 2021 field crews that were removed following discussion with the planning team due to these structures not existing, being passable, not being associated with usable habitat, or deemed not feasible to remediate because of logistic considerations."
#| warning: false
#| echo: false

data <- read.csv("data/removed-from-consideration.csv", check.names=FALSE)
prior_num <- nrow(data)
ft <- flextable(data)
ft <- format_flextable(ft)
ft
```

```{r intermediate, echo = FALSE, results = 'asis'}
#| label: tbl-intermediate
#| tbl-cap: "Updated intermediate barrier list resulting from the second barrier prioritization analysis in the Bulkley River watershed. After assessing the potential barriers on the first iteration of the intermediate list (during 2021 field season) and either identifying them as remediation priorities or eliminating them from consideration (e.g., because they passed fish or did hot have suitable habitat upstream), the remaining potential barriers in the watershed were re-prioritized. The barriers on this list were prioritized to exceed the connectivity goals of the plan. Barriers highlighted in the same colour represent sets of barriers that have been prioritized as a group. In the Barrier Status column, P = potential barrier and B = confirmed barrier. All barrier assessment data is compiled from the BC Provincial Stream Crossing Inventory System."
#| warning: false
#| echo: false

library("flextable")

data <- read.csv("data/intermediate-barriers.csv", check.names=FALSE)
inter_num <- nrow(data)
ft <- flextable(data)
ft <- format_flextable(ft)
ft
```

```{r priority, echo = FALSE, results = 'asis'}
#| label: tbl-priority
#| tbl-cap: "The Bulkley River watershed priority barrier for rehabilitation list, which includes barriers that have undergone field assessment, been reviewed by the planning team, and selected to pursue for proactive remediation."
#| warning: false
#| echo: false

library("flextable")

data <- read.csv("data/priority_barriers_for_rehabilitation_table.csv", check.names=FALSE)
rehab_num <- nrow(data)
ft <- flextable(data)
ft <- format_flextable(ft)
ft
```

Thirty barriers on the intermediate list require short-term field assessments before selection as a final barrier to pursue for restoration: 

```{r fieldreq, echo = FALSE, results = 'asis'}
#| label: tbl-fieldreq
#| tbl-cap: "Field assessment requirements for the intermediate barrier list in the Bulkley River watershed. The cost per barrier values are estimates based on previously completed field work. The habitat confirmation count is based on the assumption that the 23 barriers requiring barrier assessments will also require a subsequent confirmation. In the case that some barriers are identified as unsuitable candidates for habitat confirmations, the total cost will be reduced."
#| warning: false
#| echo: false

library("flextable")

data <- read.csv("data/field-reqs.csv", check.names=FALSE)
ft <- flextable(data)
ft <- format_flextable(ft)
ft
```

Based on the results of the prioritization analysis, 30 barriers from the intermediate barrier list are required to be remediated to achieve the connectivity goals in this plan:

```{r remcost, echo = FALSE, results = 'asis'}
#| label: tbl-remcost
#| tbl-cap: "Preliminary barrier remediation cost estimate to reach connectivity goals in the Bulkley River watershed. Cost per barrier values are estimated based on the average cost of previously completed projects. Barrier counts and total costs are subject to change as more information is collected through the implementation of this plan."
#| warning: false
#| echo: false

library("flextable")

data <- read.csv("data/remediation-cost.csv", check.names=FALSE)
ft <- flextable(data)
ft <- format_flextable(ft)
ft
```
