# Progress Reporting {-}

## Progress Reporting {-}

This WCRP was initiated in 2021. Since then, the passability of 86 structures has been assessed, and further habitat assessments were completed at 47 of these. Fish passage has been rehabilitated at 3 barriers: a collapsed bridge was removed from Robert Hatch Creek on Hatch Creek Ranch; a culvert was replaced with a clearspan bridge on McDowell Creek at Woodmere Nursery, and a culvert under Highway 16 on Taman Creek was upgraded to a larger, embedded culvert, resulting in improved or restored access to 9.65 km of spawning habitat and 31.64 km of rearing habitat for focal species. Designs for 8 additional barriers have been either completed or are underway in the watershed.    


## Rehabilitated Barriers {-}

```{r  echo = FALSE, results = 'asis'}
#| label: table-12
#| tbl-cap: "Table 12: Pacific salmon and steelhead barriers in the Bulkley River watershed that have been addressed (either through removal, replacement, or modification to improve passage) as of May 2026. Habitat gain represents the amount (km) of upstream habitat that was reconnected by these projects."
#| warning: false
#| echo: false

source("Rscripts/table_formatting.R")
library("flextable")

data <- read.csv("data/bulk_rehabilitated_barriers.csv", check.names=FALSE)
ft <- flextable(data)
ft <- format_flextable(ft)
ft
```
## Priority Barriers {-}

```{r  echo = FALSE, results = 'asis'}
#| label: table-13
#| tbl-cap: "Table 13: Structures in the Bulkley River watershed that are confirmed as barriers to fish passage for Pacific salmon and steelhead with confirmed habitat upstream, as of May 2026. Barriers known to be partially passable are indicated by “yes”, with further details provided in the adjacent column. Habitat gain represents the amount (km) of habitat upstream of that barrier to the next structure that will be reconnected if that barrier is addressed. The number of structures in a set represents the number of structures that must be addressed concurrently to maximize habitat connectivity."
#| warning: false
#| echo: false

source("Rscripts/table_formatting.R")
library("flextable")

data <- read.csv("data/bulk_priority.csv", check.names=FALSE)
ft <- flextable(data)
ft <- format_flextable(ft)
ft
```
## Annual Progress Report {-}

Since April 2025, the following actions were completed: 

 - Results of structures assessed from 2022-2024 were reviewed by the Office of the Wet-suwet’en and decisions made on next steps for each structure; 

 - Training was provided to Office of the Wet’suwet’en field technicians in barrier assessments, habitat confirmations, and electrofisher use; 

 - Owners were identified and contacted for 2 priority barriers;  

 - SSAF indicator ratings were incorporated into structure rankings, and 

 - The connectivity models was updated based on the above actions, and outputs were incorporated into this WCRP.
